Dirk Sliwka

### 2025-10-08 papers.qmd
update

<a href="assets/pdf/OSW_Final_Paper_13Feb2024.pdf" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; display: inline-block;">  PDF  </a>&nbsp;&nbsp;<button onclick="toggleAbstract('abstract-2025-Multi-rater-Performance-Evaluations-and-Incentives')" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; background: none; display: inline-block;">Abstract</button>

>>>>

<a href="assets/pdf/OSW_Final_Paper_13Feb2024.pdf" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; display: inline-block;">  PDF  </a>&nbsp;&nbsp;<a href="https://doi.org/10.1086/730321" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; display: inline-block;">  WEB  </a>&nbsp;&nbsp;<button onclick="toggleAbstract('abstract-2025-Multi-rater-Performance-Evaluations-and-Incentives')" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; background: none; display: inline-block;">Abstract</button>
